An Adolescent Mini-Neptune in the Kepler Field

### 2021-07-08 paper/ms.tex
update ms

The precision of the Kepler data itself may enable more detailed
analyses without needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-planet induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix~\ref{app:flare} highlights an odd flare
timing coincidence that may be worthy of further examination by those
more knowledgeable than us.

>>>>

The precision of the Kepler data itself may enable more detailed
analyses without needing to acquire more data.  While our transit
timing study did not yield the detection of any clearly significant
planet-planet induced TTVs, the star's flaring may be suggestive of
star-planet interactions.  Appendix~\ref{app:flare} highlights an odd
flare timing coincidence that may be worthy of further examination.

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than
    $10^9$ years are shown with gray markers.  Planets younger than a
    gigayear, with $t/\sigma_t > 3$, are shown in color.  
    \pn\ is shown with a star.
    The abnormally large radii of the youngest transiting planets
    could be explained by their primordial atmospheres not yet
    having evaporated.
    Selection effects could also be important.
    Parameters were acquired from the NASA Exoplanet Archive on July
    2, 2021.
		\label{fig:rp_period_age}
	}
\end{figure*}

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precisely measured ages spanning 10 to 100\,Myr include K2-33b,
DS~Tuc~Ab, HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet
V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
Of these systems, \pn\ inhabits a similar range of planetary size and
orbital period.  It is the smallest though ($3.6\,R_\oplus$), which
may hint at selection effects in the sample of young planets
\citep{zhou_2021_tois}.  Assuming that these planets have masses
between $\approx$10 and 20$\,M_\oplus$, their large sizes and presumed
low densities are in accord with the expectation that mini-Neptunes
start their lives with large primordial atmopsheres that are are lost
over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_core-powered_2018}.
The observation from starspot-induced TTVs that the planetary orbit
could be aligned with the stellar spin differs from a number of other
close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Overall however, it is consistent with a quiescent disk-driven
migration history for the planet, while the in-situ formation scenario
is disfavored because the necessary disk mass would always drive
planets to migrate
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.
